Holomorphic field theories and higher algebra

### 2023-07-28 highervertexops.tex
tiny additions

Two fields are {\em mutually local} if there exists a nonnegative exponent $N \in \NN^d$ such that $(z-w)^N[a(z),b(w)]$ is cohomological to zero (i.e., it is exact).

\owen{I suspect there's something better to say here, informed by your work with Nik. I'm least happy with this definition.}

>>>>

Two fields are {\em mutually local} if there exists a natural number $N \in \NN$ and an element $f(z,w)$ of the ideal $(z_i-w_i)_{i =1}^d \subset \widehat{\cO}(\DD^d\times \DD^d)$ such that $f(z,w)[a(z),b(w)]$ is cohomologous to zero (i.e., it is exact).

This condition recovers the usual notion of locality after passing to cohomology. 
\owen{I suspect there's something better to say here, informed by your work with Nik. I'm least happy with this definition.}

It is possible to formulate a representative of the ``delta function'' and one can hope that the usual formulas (e.g., describing the structure of the singular parts of commutators or OPEs) have analogs up to exact terms.
